Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2020-06-16 man/figures/0_figures_ecosystems.Rmd
update
updating

**Figure 2**. Schema of the different metrics (a) and analyses (b) used in the manuscript (see Material and methods for details). The severe drought events since 1901 were identified using SPEI-12 and characterized in terms of duration, severity and intensity. Climate impacts on vegetation were assessed for greenness and tree-growth. Non climatic disturbances on vegetation were quantified using growth changes on tree growth (% GC) and were also related with anthropogenic alterations inferred from review of historical documents. Responses of vegetation to disturbances were explored in the short- and the long-term using resilience metrics and temporal trends respectively for both EVI and BAI. Resilience metrics of BAI were computed for the eight most severe drought events since 1950, and their relationship with drought severity were explored. For the 2005 and 2012 drought events we also compared EVI and BAI resilience metrics among the three *Q. pyrenaica* populations.

@@

#####
**Figure 1**
![](../../out/fig/geomap/mapa_situacion_v2.jpg){height=750px} 
##### 
**Figure 2.**
![](../../man/figures/schema_methods/schema_analysisv3@1,5x.jpg)0

>>>>

**Figure 2**. Schema of the different metrics (a) and analyses (b) used in the manuscript (see Material and methods for details). The severe drought events since 1901 were identified using SPEI-12 and characterized in terms of duration, severity and intensity. Climate impacts on vegetation were assessed for greenness and tree-growth. Non climatic disturbances on vegetation were quantified using growth changes on tree growth (% GC) and were also related with anthropogenic alterations inferred from review of historical documents. Responses of vegetation to disturbances were explored in the short- and the long-term using resilience metrics and temporal trends respectively for both EVI and BAI. Resilience metrics of BAI were computed for the eight most severe drought events since 1950, and their relationship with drought severity were explored. For the 2005 and 2012 drought events we also compared EVI and BAI resilience metrics among the three *Q. pyrenaica* populations. Numbers (*grey circles*) indicate the study aims to which the analyses are related.

@@

**Figure 1**
![](../../out/fig/geomap/mapa_situacion_v2.jpg){height=750px}

##### 
**Figure 2.**
![](../../man/figures/schema_methods/schema_analysisv4.jpg)
